Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-21 article/article.Rmd
Commit 2024-05-21 10:14

To create a unified trend for the long term change of the clear sky irradiance, we
simulated the values of AOD derived from those sources with Libradtran. For both, we
used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
coefficients, and we choose the SZA of $55^\circ$ as a representative value for all runs.
For the first period, the alpha Ångström coefficient is $1.6$ and the beta
coefficient $0.086$ and $0.059$, for 1997 and 2005 respectively. By interpolating the
resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.
For the period 2005 -- 2005 we used the mean monthly values from AERONET, with a
similar simulation scheme. We computed the trend of clear sky radiation for each
month of the year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.

>>>>

To create a unified trend for the long term change of the clear sky irradiance, we
simulated the values of AOD derived from those sources with Libradtran. For both, we
used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
coefficients, and we choose the SZA of $55^\circ$ as a representative value for all
runs.

For the first period, the alpha Ångström coefficient is $1.6$ and the beta
coefficient $0.086$ and $0.059$, for 1997 and 2005 respectively. By interpolating the
resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.  For the
period 2005 -- 2005 we used the mean monthly values from AERONET, with a similar
simulation scheme. We computed the trend of clear sky radiation for each month of the
year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.

According to @Kazadzis2007, in the period 1997 -- 2005, the mean AOD of $340\,\text{nm}$ was calculated
to 0.403 by the Brewer spectrophotometer, with a linear trend of $-3.8±0.93\,\%$ per year.
This corresponds to a AOD $340\,\text{nm}$ change of $0.0153$ per year.
Using the alpha Ångström coefficient of $\alpha = 1.6$ this translates to a change in Ångström beta coefficient of $\beta=0.00272$ per year (or $\beta=0.084$ in 1997 and $\beta=0.059$ in 2005).

<!--
1997 0.0839901
2005 0.05496013
# Kazadzis2007 - Nine years of UV aerosol optical depth measurements at Thessaloniki, Greece
# From Stelios' paper 2007:
# AOD @340 from Brewer 086
# Period: 1997-2005
# The mean AOD for this period was calculated to 0.403 for the Brewer and 0.422 for the CIMEL.
# A linear regression on the Brewer deseasonalized data reveals a change of -3.8±0.93% per year.
# From the above data AOD @340 changes by 0.0153 per year (or 0.138 for the 9 years).
# Using Angstrom a= 1.6  this translates to a change in Angstrom β=0.00272 per year (or β=0.084 in 1997 and β=0.059 in 2005).
-->
